\documentclass[a4paper,12pt]{report}
\addtolength{\oddsidemargin}{-1.cm}
\addtolength{\textwidth}{2cm}
\addtolength{\topmargin}{-2cm}
\addtolength{\textheight}{3.5cm}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\makeindex

\usepackage{longtable}
\usepackage{graphicx}
\usepackage{makeidx}
\usepackage{hyperref}
\usepackage{verbatim}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}


% define the title
\author{Team Lima}
\title{ Assignment 1}
\begin{document}
\setlength{\parskip}{6pt}

% generates the title
\begin{titlepage}

\begin{center}
% Upper part of the page       
  
\textsc{\LARGE Department of Computer Science}\\[1.5cm]
\textsc{\Large COS 301 - Mini Project}\\[0.5cm]
% Title
\HRule \\[0.4cm]
{ \huge \bfseries Architectural Specification}\\[0.4cm]
\HRule \\[0.4cm]
% Author and supervisor
\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
Tshepo {Malesela}
\end{flushleft}
\end{minipage}
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Student number:} \\
u14211582
\end{flushright}
\end{minipage}

\vfill

{\large \today}
\end{center}
\end{titlepage}
\footnotesize
\normalsize

\renewcommand{\thesection}{\arabic{section}}

\begin{center}
\tableofcontents
\footnotesize
\normalsize  
\end{center}

\renewcommand{\thesection}{\arabic{section}}
\newpage
\begin{center}
	\textsc{\LARGE Architectural Requirement Specification}\\[1.5cm]
	\textsc{\Large Team VbScript github repository link}\\[0.5cm]
	For further references see \href{https://github.com/mfanamasimula/VBScript}{gitHub}.
	\today
\end{center}
\newpage
\subsection{Architectural Scope}
\begin{itemize}
	\item The System should be accessable at anytime while the user is on campus.
	\item The server that host the system and the database is always on.
	\item The ability to navigate a given destination on campus
	\item The system must know your current location.
	\item The system must be able to to give ...
	\item The system need to be able to host all the users on campus.
	\item Administrative users have more access to the system have CRUD capabilties on events.
	\item Each event on the system must have a destination and multiple ways of reaching that destination through the navigation.
	\item The system must have the ability to notify users of current event.
	\item Users have the ability to set a route based on user constraints such as routes with less pedestrian trafic. 
\end{itemize}
\newpage
\subsection{External Interface Requirements}
\newpage
\subsection{Performance Requirements}
\newpage
\subsection{Design Constraints}
\newpage
\subsection{Software System Attributes}
\newpage
\subsection{UML Design}
\subsubsection{Domain Model}
\subsubsection{Package Diagrams}
\textbf{Navigation Module} \\
\textbf{Events}\\
\textbf{Notification Module}\\
\textbf{GIS Module}
\subsubsection{Class diagrams}
\textbf{Navigation Module}\\
\textbf{Events}\\
\textbf{Notification Module}\\
\textbf{GIS Module}
\subsubsection{Package Diagrams}
\textbf{Navigation Module}\\
\textbf{Events}\\
\textbf{Notification Module}\\
\textbf{GIS Module}
\subsubsection{Activity Diagrams}
\textbf{Navigation Module}\\
\textbf{Events}\\
\textbf{Notification Module}\\
\textbf{GIS Module}\\

\newpage
\subsection{Design Patterns}
\newpage
\subsection{Technology}
\newpage
\subsection{Quality and Feasability Design}
\end{document}